Meta-analysis of fungicide application timing experiments for powdery mildew management

### 2020-02-28 06_Publication_wireframe_and_7_Questions.Rmd
editing and writing

Commercially available mungbean cultivars in Australia lack sufficient resistance to be used as a sole powdery mildew management strategy.
Quantitative disease resistance has been observed in some breeding lines [@Pandey2018; @Chankaew2013]. 
In Australia there are very few availble powdery mildew resistant cultivars. 
Jade-AU is recommended as containing the best disease resistance to powdery mildew and other foliar diseases, such as tan spot and halo blight.
However other disease management strategies, such as fungicides, are still required [@Kelly2017a].

Treatment of powdery mildew in mungbean with fungicide is currently an effective method for reducing the impact of the disease.

>>>>

Commercially available mungbean cultivars in Australia lack sufficient resistance to be used as a sole powdery mildew management strategy.
Quantitative disease resistance has been observed in some breeding lines [@Pandey2018; @Chankaew2013]. 
In Australia there are very few availble powdery mildew resistant cultivars. 
Jade-AU is recommended as containing the best disease resistance to powdery mildew (moderately susceptible), and other foliar diseases, such as tan spot and halo blight [@AustralianMungbeanAssociation].
However other disease management strategies, such as fungicides, are still required [@Kelly2017a].

Treatment of powdery mildew in mungbean with fungicide is currently an effective method for reducing the impact of the disease. 
Past field trials in eastern Australia have trialed a range of fungicides, some of which have been registered with the APVMA (Australian Pes.....) for treating powdery mildew in mungbean [@Kelly2017a; insert all published trials here].
